### 2022-08-03 main/chapter_2ljets.tex
add cls clsb clb commands

At each parameter point of a signal model, it is added to the background model
and tested against data in the $\mathrm{CLs}$ prescription.
Contours showing which parameters of those signal models are labelled as
excluded are displayed for
C1N2 in Figure~\ref{fig:2ljets_contours_c1n2} and for
GMSB in~\ref{fig:2ljets_contours_gmsb}.

@@

% exclusion plots
\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_c1n2.pdf}
\caption[
Contours for the C1N2 model in the $\twoljets$-electroweak analysis
]{%
Contours for the C1N2 model in the $\twoljets$-electroweak
analysis~\cite{atlas2022searches}.
\\[0.5em]
Space below the solid red line is labelled as excluded, and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
\\[0.5em]
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Grey areas are observed limits from the two-lepton parts
of~\cite{atlas_23l_SUSY_2016_24} and~\cite{atlas_2l_SUSY_2013_11}.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_c1n2}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_gmsb.pdf}
\caption[
Contours for the GMSB model in the $\twoljets$-electroweak analysis
]{%
Contours for the GMSB model in the $\twoljets$-electroweak
analysis~\cite{atlas2022searches}.
\\[0.5em]
Space below the solid red line is labelled as excluded, and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
\\[0.5em]
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Exclusion is defined by the $95\%$ $\mathrm{CLs}$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_gmsb}
\end{figure}

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lcccccc}
& \multicolumn{2}{c}{Fitted}
& Data
& $A\epsilon\sigma_{\mathrm{obs}}^{95}~\mathrm{fb}$
& $S_{\mathrm{obs}}^{95}$
& $S_{\mathrm{exp}}^{95}$
& $\mathrm{CLb}$
& $p_{s\!=\!0}$
\\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & $21$ & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$
\\[.5ex]
DR-Low & $22$ & $4$ & $18$ & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$
\\[.5ex]
DR-Int & $35$ & $4$ & $38$ & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$
\\[.5ex]
DR-High & $3.9$ & $0.5$ & $0$ & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0$ & $0.50$
\\[.5ex]
DR-$\llbb$ & $0.51$ & $0.20$ & $0$ & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$
\\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\mathrm{CLs}$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\\
\TODO{add labels and references to asymptotic formulae paper}
\\
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, the general message has not changed.
Values of CLs from mean data in the combined fit are overlaid on the grid.
}
\label{fig:2ljets_fit_muti_contourss}
\end{figure}

>>>>

At each parameter point of a signal model, it is added to the background model
and tested against data in the $\cls$ prescription.
Contours showing which parameters of those signal models are labelled as
excluded are displayed for
C1N2 in Figure~\ref{fig:2ljets_contours_c1n2} and for
GMSB in~\ref{fig:2ljets_contours_gmsb}.

@@

% exclusion plots
\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_c1n2.pdf}
\caption[
Contours for the C1N2 model in the $\twoljets$-electroweak analysis
]{%
Contours for the C1N2 model in the $\twoljets$-electroweak
analysis~\cite{atlas2022searches}.
\\[0.5em]
Space below the solid red line is labelled as excluded, and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
\\[0.5em]
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Grey areas are observed limits from the two-lepton parts
of~\cite{atlas_23l_SUSY_2016_24} and~\cite{atlas_2l_SUSY_2013_11}.
Exclusion is defined by the $95\%$ $\cls$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_c1n2}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_contours_gmsb.pdf}
\caption[
Contours for the GMSB model in the $\twoljets$-electroweak analysis
]{%
Contours for the GMSB model in the $\twoljets$-electroweak
analysis~\cite{atlas2022searches}.
\\[0.5em]
Space below the solid red line is labelled as excluded, and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
\\[0.5em]
The yellow band shows the $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the prior distribution of the test statistic.
Exclusion is defined by the $95\%$ $\cls$ prescription
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours_gmsb}
\end{figure}

% upper limits
% definitely want this after pictures
\FloatBarrier
\begin{table}[tp]
\centering
% custom separator for aligned +-
% https://stackoverflow.com/a/2132998
\begin{tabular*}{\textwidth}{lr@{$~\pm~$}lcccccc}
& \multicolumn{2}{c}{Fitted}
& Data
& $A\epsilon\sigma_{\mathrm{obs}}^{95}~\mathrm{fb}$
& $S_{\mathrm{obs}}^{95}$
& $S_{\mathrm{exp}}^{95}$
& $\mathrm{CLb}$
& $p_{s\!=\!0}$
\\[1.5ex]
DR-OffShell & $22.1$ & $2.7$ & $21$ & $0.10$ & $14.3$ & $12.3^{+4.7}_{-3.1}$ & $0.68$ & $0.50$
\\[.5ex]
DR-Low & $22$ & $4$ & $18$ & $0.08$ & $10.8$ & $15.3^{+5.7}_{-4.0}$ & $0.09$ & $0.50$
\\[.5ex]
DR-Int & $35$ & $4$ & $38$ & $0.15$ & $20.9$ & $17.5^{+5.9}_{-3.9}$ & $0.73$ & $0.23$
\\[.5ex]
DR-High & $3.9$ & $0.5$ & $0$ & $0.02$ & $3.0$ & $5.6^{+2.2}_{-1.5}$ & $0$ & $0.50$
\\[.5ex]
DR-$\llbb$ & $0.51$ & $0.20$ & $0$ & $0.02$ & $3.0$ & $3.0^{+1.3}_{-0.0}$ & $0.19$ & $0.50$
\\[.5ex]
\end{tabular*}
\caption[
Upper limit results in $\twoljets$-electroweak discovery regions
]{%
Upper limit results in $\twoljets$-electroweak discovery
regions~\cite{atlas2022searches}.
The fitted yield is in the background-only model constrained by the data in each region.
Limits are intended to reflect constrains on additive signal contributions.
\\[0.5em]
Left to right:
the region name,
the post-fit background expectation,
the number of data observed,
the observed $95\%$ $\cls$ upper limit on the visible cross-section
$\langle\epsilon\sigma\rangle_\mathrm{obs}^{95}$,
its corresponding signal expectation $S_\mathrm{obs}^{95}$,
the expected $95\%$ upper limits on the signal expectation $S_\mathrm{exp}^{95}$
as would be obtained were the test statistic given by its central or
$\pm1$-sigma variations,
$\mathrm{CLb}$ evaluated with the signal expectation set to the observed upper limit,
and the discovery $p$-value (capped at $0.5$) with its equivalent significance.
\\[0.5em]
Upper limits use the one-sided profile likelihood test statistic.
The discovery $p$-value uses a profile likelihood test statistic in a one-sided test.
All $p$-values are estimated by simulation of alternative data.
\\
\TODO{add labels and references to asymptotic formulae paper}
\\
\TODO{reference pdg rounding}
}
\label{tab:2ljets_discovery}
\end{table}

@@

\begin{figure}[tp]
\centering
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_c1n2.pdf}
\caption{C1N2}
\end{subfigure}
\hfill
\begin{subfigure}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_fit_multi_contours_gmsb.pdf}
\caption{GMSB}
\end{subfigure}
\caption[
Projected exclusion from sets of orthogonal signal regions
]{%
Projected exclusion from sets of orthogonal signal regions, demonstrating that
their combination has greater sensitivity reach than any individually.
The label `High' indicates the bins of SR-High, and `HighNo4' excludes
SR-High-1J to show the locations where mono-jet events have an impact.
Similarly, `$\llbb$', `Int', `Low', and `OffShell' are shown to target their
appropriate parameter spaces.
Although figures were produced before unblinding, with older samples and region
designs, the general message has not changed.
Values of $\cls$ from mean data in the combined fit are overlaid on the grid.
}
\label{fig:2ljets_fit_muti_contourss}
\end{figure}
